Probabilistic Forecast Reconciliation

### 2018-11-12 Presentation/ProbForeRec.tex
More slides added to pres

\documentclass{beamer}
\usetheme{Warsaw}
\usepackage{amsmath,amsthm, bm, tikz,qtree}
\usetikzlibrary{arrows,positioning,shapes,fit,calc}
\usepackage[greek,english]{babel}

@@

    \item Wind power

@@

    	\item Daily series is aggregate of 24 hourly series.  

@@

@@

  \begin{frame}{Reconciliation}

@@

    	\only<2>{\item Let {\color{blue}$m$} be the number of bottom level series and {\color{blue}$\bm{b}_t$} be an {\color{blue}$m$}-vector of the bottom level series.}

@@

  {\bm y}={\bm S}{\bm b}

@@

@@

   \begin{frame}{Looking ahead}

@@

        \item Further development of multivariate scoring rules.

@@

>>>>

\documentclass{beamer}
\usetheme{Warsaw}
\usepackage{amsmath,amsthm, bm, tikz,qtree,multirow,booktabs}
\usetikzlibrary{arrows,positioning,shapes,fit,calc}
\usepackage[greek,english]{babel}

@@

    \item Wind power \hyperlink{aelos}{\beamerbutton{}}

@@

    	\item Daily series is aggregate of 24 hourly series.\label{afterdat}  

@@

  \hfill\hyperlink{bu}{\beamerbutton{}}

@@

  \begin{frame}{Reconciliation}\label{cont}

@@

    	\pause\item Let {\color{blue}$m$} be the number of bottom level series and {\color{blue}$\bm{b}_t$} be an {\color{blue}$m$}-vector of the bottom level series.

@@

  {\bm y}_t={\bm S}{\bm b}_t

@@

   \hfill\hyperlink{sim}{\beamerbutton{}}

@@

   \begin{frame}{Looking ahead}\label{simdisc}

@@

@@

    \Huge{Thank You!}\\
  \pause\Huge{Questions?}
  \begin{frame}{Aeolos Wind Farm}\label{aelos}
  \includegraphics[height=7cm]{Figs/Aeolos_Unscaled}
  \begin{frame}{Aeolos Wind Farm}
  \includegraphics[height=7cm]{Figs/Aeolos_Unscaled}
  \begin{frame}{Aeolos Wind Farm}
\includegraphics[height=7cm]{Figs/Aeolos_Scaled}
  \hfill\hyperlink{afterdat}{\beamerbutton{}}
  \begin{frame}{What we do NOT do}\label{bu}
  	\item All information is contained in the most disaggregate series.
  	\item In principle using the correct multivariate model for the most disaggregate series and aggregating them should work.
  	\item Disaggregate series are: 
  		\item Very noisy
  		\item High-dimensional
  		\item Prone to model misspecification
  \hfill\hyperlink{cont}{\beamerbutton{}}
  \begin{frame}{Simulation Results}\label{sim}
  Hierarchy from earlier bottom series are ARIMA models.  Training sample of 500, one-step ahead forecasts, 1000 replications.
  \begin{table}
  	\centering\small
  	\begin{tabular}{lccc}
  		\toprule
  		Forecasting &{\text{Energy score}} & {\text{Variogram score}} & {\text{Log score}} \\
  		\midrule
  		MinT(Sample) &  {\bf 10.01}   & {\bf 8.41}  & {\bf 11.29} \\
  		OLS          &  10.53   & 8.86  & 11.54 \\
  		Bottom-up    &  12.35   & 9.22  & 12.05 \\
  		Incoherent	 &  11.12   & 9.53  \\
  		\bottomrule
  	\end{tabular}
  \end{table}
\hfill\hyperlink{simdisc}{\beamerbutton{}}
